---
title: "Exercises about hierarchies, removeEmpty and removeCodes"
author: ""
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{frekvens-kurs-oppgaver}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA
)

```


If you run the following code, you can use a `Print` function
This function might make  inspecting the output of GaussSuppression
easier by replacing FALSE with - in the suppressed and primary columns.

`source("/R/Print.R")`


```{r}
source("../R/Print.R")
```



### Exercise 1

Load the dataset `sdc_cars` and take a look at it. Tip: `load("data/sdc_cars.RData")`

Run this analysis:

```
  SuppressDominantCells(sdc_cars, 
                        n = 1:2, k = c(85, 95), 
                        numVar = "value", 
                        dimVar = c("sector", "k_group"), 
                        contributorVar = "car_brand")
```


How many rows are in the output?

```{r}
load("../data/sdc_cars.RData")
head(sdc_cars, 10) # 10 First
sdc_cars[sample.int(nrow(sdc_cars), 20), ] # 20 random
tail(sdc_cars, 10) # 10 Load
```



#### Solution
20 rows in the output


```{r}
library(GaussSuppression)
out1 <- SuppressDominantCells(sdc_cars,
                               n = 1:2, k = c(85, 95),
                               numVar = "value",
                               dimVar = c("sector", "k_group"),
                               contributorVar = "car_brand")
Print(out1)
```


### Exercise 2

Run the same analysis with the formula interface.
Does it appear that the output is the same?


#### Solution

One row is missing. This has 0 contributions. Otherwise similar, but different sorting.



```{r}
out2 <- SuppressDominantCells(sdc_cars,
                               n = 1:2, k = c(85, 95),
                               numVar = "value",
                               formula = ~sector*k_group,
                               contributorVar = "car_brand")
Print(out2)
```




### Exercise 3

Run the analyzes in Exercise 1 and 2 again and include the `removeEmpty` parameter. 
This can be `TRUE` or` FALSE`. 
Use the parameter in such a way that you do not get the same answer as before.


```{r}
out3a <- SuppressDominantCells(sdc_cars,
                               n = 1:2, k = c(85, 95),
                               numVar = "value",
                               dimVar = c("sector", "k_group"),
                               contributorVar = "car_brand",
                               removeEmpty = TRUE)
Print(out3a)

out3b <- SuppressDominantCells(sdc_cars,
                               n = 1:2, k = c(85, 95),
                               numVar = "value",
                               formula = ~sector*k_group,
                               contributorVar = "car_brand",
                               removeEmpty = FALSE)
Print(out3b)

```



### Exercise 4

Continue with formula interface using `"sector"` and `"k_group"`, but now switch to `SuppressFewContributors` with `maxN = 2`.
Also include `removeEmpty = FALSE`.

Do you see that you get the same answer as in Exercise 3?


```{r}
out4 <- SuppressFewContributors(sdc_cars,
                                 maxN = 2,
                                 numVar = "value",
                                 formula = ~sector*k_group,
                                 contributorVar = "car_brand",
                                 removeEmpty = FALSE)
Print(out4)

```





### Exercise 5


Run one of the analyzes from Exercises 1-3 again, but make a change in `k` so that you get a different result for the suppression.


```{r}
library(GaussSuppression)
out5 <- SuppressDominantCells(sdc_cars,
                               n = 1:2, k = c(70, 80),
                               numVar = "value",
                               dimVar = c("sector", "k_group"),
                               contributorVar = "car_brand")
Print(out5)
```




### Exercise 6

We will continue with roughly the same problems

Run this analysis:

```
  SuppressFewContributors(sdc_cars, 
                          maxN = 2, 
                          numVar = "value", 
                          dimVar = c("sector", "k_group"), 
                          contributorVar = "car_brand")
```

What is the difference between the numbers in `freq`, `nRule` and `nAll`?

#### Solution

   * *freq:* Number of rows that have been summed
   * *nRule=nAll:* Number of `car_brand` included in the sum

```{r}
out6 <- SuppressFewContributors(sdc_cars,
                                 maxN = 2,
                                 numVar = "value",
                                 dimVar = c("sector", "k_group"),
                                 contributorVar = "car_brand",
                                 removeEmpty = FALSE)
Print(out6)
```


### Exercise 7

Make a change in the analysis in Exercise 6 that takes into account that all the figures from Tesla and Hyundai are openly available. Use the `removeCodes` parameter for this.

What is the difference between the numbers in `nRule` and `nAll` now?

#### Solution

   * *nAll:* Number of `car_brand`'s included in the sum
   * *nRule:* Number of `car_brand`'s that is counted in the suppression rule. What is open (Tesla and Hyundai) is not counted.



```{r}
out7 <- SuppressFewContributors(sdc_cars,
                                 maxN = 2,
                                 numVar = "value",
                                 dimVar = c("sector", "k_group"),
                                 contributorVar = "car_brand",
                                 removeEmpty = FALSE,
                                 removeCodes = c("Tesla", "Hyundai"))
Print(out7)
```



### Exercise 8


Run the analysis in Exercise 1 again with a modification where you no longer use the `dimVar` parameter, but instead use `hierarchies`. What you need for the `hierarchies` parameter can be generated with either `FindDimLists` or `FindHierarchies` in the `SSBtools` package. 

How should `FindDimLists` or `FindHierarchies` be executed?

Take a look at the results from `FindDimLists` or `FindHierarchies`. 
Do you see that the output from `SuppressDominantCells` is the same as in Exercise 1?

```{r}
library(SSBtools)

diml <- FindDimLists(sdc_cars[c("sector", "k_group")])
diml

hier <- FindHierarchies(sdc_cars[c("sector", "k_group")])
hier


out8a <- SuppressDominantCells(sdc_cars,
                               n = 1:2, k = c(85, 95),
                               numVar = "value",
                               hierarchies = diml,
                               contributorVar = "car_brand")

Print(out8a)

out8b <- SuppressDominantCells(sdc_cars,
                               n = 1:2, k = c(85, 95),
                               numVar = "value",
                               hierarchies = hier,
                               contributorVar = "car_brand")

Print(out8b)
```{r}
