---
title: "Exercises with the SmallCountRounding package"
author: ""
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{frekvens-kurs-oppgaver}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA
)

```





### Exercise 1

Load the dataset `pregnant_micro`. Tip: `load("data/pregnant_micro.RData")`

Run this analysis:
```
PLSroundingPublish(pregnant_micro, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant)
```

Also try `removeEmpty = FALSE`

What is the difference?

**Correction:** We have changed from  `roundBase = 5` to `roundBase = 5` 
                so that the results are more interesting

```{r}
load("../data/pregnant_micro.RData")
pregnant_micro
```

#### Solution

With `removeEmpty = FALSE`, five extra rows of zeros are included. This is as in the suppression functions.

**Note:** With  `roundBase = 3`, the `rounded` values are equal to the `original` values for all rows, as there are neither ones nor twos present.


```{r}

library(SmallCountRounding)

PLSroundingPublish(pregnant_micro, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant)

PLSroundingPublish(pregnant_micro, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   removeEmpty = FALSE)

```



### Exercise 2

Load the dataset `pregnant`. Tip: `load("data/pregnant.RData")`



Use this dataset and run the same analyses?

How should this be done?

What is the difference in the results?



```{r}
load("../data/pregnant.RData")
pregnant
```

#### Solution

Now it is important to use `freqVar = "freq"`

With `removeEmpty = FALSE`, the results remain unchanged.
With default (`removeEmpty = TRUE`), three extra rows of zeros are included. 
This corresponds to the non-structural zeros in the input data. 

*Note:* Even better to include `preAggregate = TRUE`. See Exercise 4. 


```{r}
PLSroundingPublish(pregnant, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   freqVar = "freq")

PLSroundingPublish(pregnant, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   freqVar = "freq",
                   removeEmpty = FALSE)

```




### Exercise 3

Create a new dataset with this code:

```
pregnant2 <- SSBtools::Extend0(pregnant[-3])
```

Repeat exercise 2 with this data set.


```{r}
load("../data/pregnant.RData")

pregnant2 <- SSBtools::Extend0(pregnant[-3])

pregnant2
```

#### Solution

Again it is important to use `freqVar = "freq"`

With default (`removeEmpty = TRUE`), now same answer as `removeEmpty = FALSE`.

Since all zeros, structural and non-structural, are included in input.  

*Note:* Even better to include `preAggregate = TRUE`. See Exercise 4. 


```{r}

PLSroundingPublish(pregnant2, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   freqVar = "freq")

PLSroundingPublish(pregnant2, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   freqVar = "freq",
                   removeEmpty = FALSE)

```


### Exercise 4

Look at the inner data sets obtained by 
`PLSroundingInner` instead of `PLSroundingPublish` in Exercises 1-3.

What are the differences?


#### Solution that applies to all exercises

`removeEmpty = FALSE` has no effect on inner cells. 


##### *Exercise 1*


#### Solution

Inner cells are aggregated input data with `original`, `rounded` and `difference`.


```{r}

PLSroundingInner(pregnant_micro, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant)

PLSroundingInner(pregnant_micro, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   removeEmpty = FALSE)

```


##### *Exercise 2*


#### Solution

Inner cells are as input, not aggregated,  without `age` and with `original`, `rounded` and `difference`.
Several combinations are on several rows, since several age categories. 

Since data is not properly aggregated, it is better to include `preAggregate = TRUE`.


```{r}
PLSroundingInner(pregnant, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   freqVar = "freq")

```



#### Solution

As the *Exercise 2* solution above.


##### *Exercise 3*



```{r}

PLSroundingInner(pregnant2, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   freqVar = "freq")
```



### *Exercise 4*  with  `preAggregate = TRUE`


##### *Exercise 2* with  `preAggregate = TRUE`


```{r}
PLSroundingInner(pregnant, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   freqVar = "freq",
                   preAggregate = TRUE)

```



##### *Exercise 3* with  `preAggregate = TRUE`



```{r}
PLSroundingInner(pregnant2, 
                   roundBase = 5, 
                   formula = ~municipality*gender*pregnant,
                   freqVar = "freq",
                   preAggregate = TRUE)

```




### Exercise 5

Would you say it is safe or recommended to use `zeroCandidates = TRUE` in any of the analyses above?

This is a theory exercise. You do not need to run the analyses.



#### Solution


##### *Exercise 1*, `pregnant_micro`:

No zeros in inner cells.  
`zeroCandidates = TRUE` will have no effect.


##### *Exercise 2*, `pregnant`:

Non-structural zeros in inner cells.  

With `zeroCandidates = TRUE`, corresponding zeros in output may be “rounded up”.

This approach is recommended for improved confidentiality protection


##### *Exercise 3*, `pregnant2`:


Now also, structural zeros in inner cells.  

With `zeroCandidates = TRUE`, corresponding structural zeros in output may be “rounded up”.

This approach is not advised because assigning non-zero values to structural zeros may lead to misleading or confusing interpretations of the data.



